Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-02-04 manuscript.tex
lastest version

The Last two methods was implemented and are available as a free software on the Hazard Modeling Toolkit (HMTK) from GEM Foundation.

All the hazard calculations was performed on OpenQuake \citep{pagani_2014} open source software.

@@

In the case of Brazilian catalog the methods did not present large differences at the final number of earthquakes (fig. \ref{fig_decluster}a) and the Gardner-Knopof/Uhrhammer combination was chosen to maximize the number of events.

@@

The model is completely defined by \gls{sym:k_cnn}, \gls{sym:a_cnn} and \gls{sym:Rmin}. To optimize these parameters the catalog is divided in two parts: one for learning about the parameters and other to test them. The target catalog will able us to check the model prediction performance derived from its chosen parameters. The best model parameters will maximize the prediction model capacity likely the target catalog.

@@

Then, over all cells, the log-likelihood, to be maximized, between model (from the learning catalog) prediction and earthquakes observed (on testing catalog) is written as
\begin{equation}
	\ensuremath{
		\gls{sym:L} = \sum_{i_x=1}^{N_x}\sum_{i_y=1}^{N_y}\log p\left[  \gls{sym:Np}, \gls{sym:nxy}  \right]
	}
	\label{eq:loglik}
\end{equation}
where \gls{sym:Np} is the \glsdesc{sym:Np} and
	  \gls{sym:nxy} is the \glsdesc{sym:nxy}.

@@

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_catalogues}
	\caption{Learning and target catalogs.}
	\label{fig_helmstetter_catalogues}
\end{figure}

>>>>

The last two methods was implemented and are available as a open source software on the Hazard Modeling Toolkit (HMTK) from Global Earthquake Model (GEM) Foundation.

All the hazard calculations was performed on OpenQuake \citep{pagani_2014} open source software also from GEM Foundation.

@@

In the case of Brazilian catalog the methods did not present large differences at the final number of earthquakes (fig. \ref{fig_decluster}a) and the Gardner-Knopoff/Uhrhammer combination was chosen to maximize the number of events.

@@

The model is completely defined by \gls{sym:k_cnn}, \gls{sym:a_cnn} and \gls{sym:Rmin}. To optimize these parameters the catalog is divided in two parts: one for \emph{learning} about the parameters and other to test them. The \emph{testing} catalog will able us to check the model prediction performance derived from its chosen parameters. The best model parameters will maximize the prediction model capacity likely the target catalog.

@@

Then, over all cells, the log-likelihood, to be maximized, between model prediction (from the learning catalog) and the observed earthquakes (on the testing catalog) is written as
\begin{equation}
	\ensuremath{
		\gls{sym:L} = \sum_{i_x=1}^{N_x}\sum_{i_y=1}^{N_y}\log p\left[  \gls{sym:Np}, \gls{sym:nxy}  \right]
	}
	\label{eq:loglik}
\end{equation}
where \gls{sym:Np} is the \glsdesc{sym:Np} and
	  \gls{sym:nxy} is the \glsdesc{sym:nxy}.

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_woo_kernels}
	\caption{\citet{kagan_knopoff_1980} kernel shapes for some magnitude values.}
	\label{fig_woo_kernels}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_catalogues}
	\caption{Learning and testing catalogs.}
	\label{fig_helmstetter_catalogues}
\end{figure}
